%-------------------------
% Resume in Latex
% Author : Gabriel Sison
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Random Stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\evensidemargin}{-0.45in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Commands  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-3pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Heading  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
    \begin{center}
        % NAME
        {\Huge\scshape Andreas Neacsu} 
        \\
        % SUBHEADING
        \small
        % EMAIL
        \href{mailto:andreasneacsu@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{andreasneacsu@gmail.com}} ~ 
        % LINKEDIN
        \href{https://www.linkedin.com/in/andreas-neacsu}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/andreas-neacsu}}  ~
        % GITHUB
        \href{https://www.github.com/andreas-04}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/andreas-04}}
    \end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Education  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.48\textwidth}
  \section{Education}
    \resumeSubHeadingListStart
    
      % MAIN INFORMATION
      \resumeSubheading
      {University Of Idaho}{Moscow, ID}
      {B.S Computer Science, 3.57 GPA}{May, 2026}
    \resumeSubHeadingListEnd
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
  \section{Technical Skills}
      \vspace{-7pt}
      \begin{itemize}
      [leftmargin=0.15in, label={}]\small{\item{
          % LANGUAGES
          \textbf{Languages}{: Go, Python, JavaScript, TypeScript, C++} \\
          \textbf{Developer Tools}{: Git, Unix, Docker, Kubernetes}}}
      \end{itemize}
\end{minipage}

\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading {Associate Software Engineer}{June 2025 - Present}
        {Schweitzer Engineering Laboratories}{}
            \resumeItemListStart
    \resumeItem{Built an internal code generation tool that creates complete Go microservices 
    directly from .proto files, reducing service bootstrap time from days to minutes and 
    shipping as part of an internal SDK release.}

    \resumeItem{Applied hexagonal architecture patterns to generate clean, maintainable service 
    layers across HTTP, gRPC, and WebSocket transports.}

\resumeItem{Diagnosed recurring system instability in CI virtual machines and built a 
system readiness endpoint that automated pre-run health validation, unblocking 
a 15+ person development team and reducing failed pipeline runs.}

    \resumeItem{Partnered with engineers across multiple product groups to surface recurring 
    workflow pain points and drive feature enhancements aligned with real development needs.}
    
\resumeItemListEnd
        \resumeSubheading {Software Engineering Intern}{October 2024 - June 2025}{Schweitzer Engineering Laboratories}{}
            \resumeItemListStart
                \resumeItem{Shipped production-ready frontend features for a containerized React microservice, using MobX to improve state consistency, responsiveness, and user workflow clarity.}
                
                \resumeItem{Developed and maintained Cypress end-to-end test suites, increasing test reliability and preventing regressions across high-traffic user flows.}
                
                \resumeItem{Implemented CI/CD pipeline caching for unit tests, reducing build times by up to 30\% and speeding up iteration for the entire development team.}
                
                \resumeItem{Collaborated with senior engineers in an Agile environment through design discussions, code reviews, and cross-service integration work.}
                
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PROJECTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Personal Projects} 
    \resumeSubHeadingListStart
\resumeSubheading{TerraCrate}{August 2025 - May 2026}
    {Capston Senior Design Project}{}
    \resumeItemListStart
        \resumeItem{Designed and implemented a Flask REST API with JWT session management and 
        attribute-based access control handling file management, user administration, 
        and system configuration for a self-hosted file-sharing platform.}
        
        \resumeItem{Engineered an mTLS authentication layer using a self-signed CA, nginx reverse 
        proxy, and automated X.509/PKCS\#12 certificate delivery via SMTP, enabling 
        zero-trust client verification.}
        
        \resumeItem{Implemented full-disk encryption on a Raspberry Pi using LUKS with custom 
        systemd service orchestration to ensure secure startup sequencing on constrained hardware.}
        
        \resumeItem{Deployed a multi-service architecture via Docker Compose with persistent 
        volumes, custom Docker daemon DNS configuration, and an admin-controlled invite system with domain allowlisting.}
        
        \resumeItem{Built a React/TypeScript frontend with role-aware UI rendering and a 
        real-time admin dashboard for user, group, and system management.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd
\section{Extracurricular Activities}
    \resumeSubHeadingListStart
        \resumeSubheading{Association for Computing Machinery}{January 2023 - December 2023}{Chapter President - University of Idaho}{}
            \resumeItemListStart
                \resumeItem{Led the University of Idaho ACM chapter, organizing events and initiatives that increased membership by 25\% and improved community engagement.}
                \resumeItem{Hosted workshops on portfolio building and technical interview preparation, helping members strengthen their professional skill sets.}
            \resumeItemListEnd
        \resumeSubheading{Idaho Quantitative Traders} {August 2025 - Present}{Member}{}
            \resumeItemListStart
                \resumeItem{Contributed to the development of a Go-based strategy backtesting system, enabling simulation, performance analysis, and iteration on algorithmic trading logic.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\end{document}